A Hitchhiker's Guide to Reproducible Research in R

### 2021-07-05 manuscript.Rmd
note Maximilians contribution
close #127

Defining the research questions and planning data analysis before observing the research outcomes is called preregistration [https://www.pnas.org/content/115/11/2600].
Preregistration increases the credibility of empirical results in three ways [preregistration is hard and worthwhile, Nosek].

>>>>

Defining the research questions and planning data analysis before observing the research outcomes is called preregistration [@NosekRevolution2018].
Preregistration increases the credibility of empirical results in three ways @nosekPreregistrationHardWorthwhile2019:
